Specification of Advanced Types Translation

### 2014-03-27 DOCUMENTATION/AdvancedTypes.tex
Fixing the rule CAST

\begin{align*}
&\trad{n}{ShiftExp} \isdef \LET p \sep v \sep t  = \trad{n}{Exp} \AND \\ \\
&\quad iStart \sep iEnd \sep iType = \trad{n}{TSymbol}  \AND  \ell = \lbl \IN \\
&\quad \IF ( iStart == 0 ) \THEN  \llvm{",\PH{t} \PH{v} "} \sep p \\
&\quad \ELSE \LET  p \sep v \sep v' \sep t'  = \trad{p,t,v,itype,istart}{Cast} \IN \\
&\quad \llvm{",\PH{t} \PH{l} "} \sep  \llvm{"\PH{p} \PH{\ell} = sub \PH{t'} \PH{v}, \PH{v'}\nl"}  \\
\end{align*}

@@

\begin{align*}
&\trad{p,t,v,t',v'}{Cast} \isdef \LET  \ell = \lbl \IN \\
&\quad \IF ( t == t') \THEN p \sep v \sep v' \sep t  \\
&\quad \ELSE \IF (t<t') \THEN \\
&\quad \quad \llvm{"\PH{p} \PH{l}= bitcast \PH{t} \PH{v} , \PH{t'}\nl"}  \sep l \sep v' \sep t'\\ 
&\quad \ELSE \\ 
&\quad \quad \llvm{"\PH{p} \PH{l}= bitcast \PH{t'} \PH{v'} , \PH{t}\nl"} \sep v \sep l \sep t \\ 
\end{align*}

>>>>

\begin{align*}
&\trad{n}{ShiftExp} \isdef \LET p \sep v \sep t  = \trad{n}{Exp} \AND \\ \\
&\quad iStart \sep iEnd \sep iType = \trad{n}{TSymbol}  \AND  \PH{\ell} = \lbl \IN \\
&\quad \IF ( iStart == 0 ) \THEN  \llvm{",\PH{t} \PH{v} "} \sep p \\
&\quad \ELSE \LET  p' \sep v \sep v' \sep t'  = \trad{t,v,itype,istart}{Cast} \IN \\
&\quad \llvm{",\PH{t} \PH{\ell} "} \sep  \llvm{"\PH{p} \PH{p'}  \PH{\ell} = sub \PH{t'} \PH{v}, \PH{v'}\nl"}  \\
\end{align*}

@@

\begin{align*}
&\trad{t,v,t',v'}{Cast} \isdef \LET  \ell = \lbl \IN \\
&\quad \IF ( t == t') \THEN p \sep v \sep v' \sep t  \\
&\quad \ELSE \IF (t<t') \THEN \\
&\quad \quad \llvm{"\PH{\ell}= bitcast \PH{t} \PH{v} , \PH{t'}\nl"}  \sep l \sep v' \sep t'\\ 
&\quad \ELSE \\ 
&\quad \quad \llvm{"\PH{\ell}= bitcast \PH{t'} \PH{v'} , \PH{t}\nl"} \sep v \sep l \sep t \\ 
\end{align*}
